Formula translation in C++, Python and modern Fortran: a~case~study~of~the~language~choice tradeoffs

### 2013-07-17 paper/doc/paper.tex
adding mention of C++11 and F2008 in the abstract

    \begin{abstract}
        Three object-oriented implementations of a prototype solver of the advection equation are introduced.
        The presented programs are based on Blitz++ (C++), NumPy (Python), and Fortran's built-in array containers.
        The solvers constitute implementations of the Multidimensional Positive-Definite 
          Advective Transport Algorithm (MPDATA).
        The introduced codes serve as examples for how the application of 
          object-oriented programming (OOP) techniques allows to reproduce the mathematical notation 
          used in the literature within the program code.
        A discussion on the tradeoffs of the programming language choice is presented.
        The main angles of comparison are code brevity and syntax clarity
          (and hence maintainability and auditability) as well as performance.
        All performance tests are carried out using free and open-source compilers.
        In the case of Python, a significant performance gain is observed when switching from the standard 
          interpreter (CPython) to the PyPy implementation of Python.
        Entire source code of all three implementations is embedded in the text and is licensed
          under the terms of the GNU GPL license.

>>>>

    \begin{abstract}
        Three object-oriented implementations of a prototype solver of the advection equation are introduced.
        The presented programs are based on Blitz++ (C++), NumPy (Python), and Fortran's built-in array containers.
        The solvers constitute implementations of the Multidimensional Positive-Definite 
          Advective Transport Algorithm (MPDATA).
        The introduced codes serve as examples for how the application of 
          object-oriented programming (OOP) techniques and new language constructs from
          C++11 and Fortran 2008 allow to reproduce the mathematical notation 
          used in the literature within the program code.
        A discussion on the tradeoffs of the programming language choice is presented.
        The main angles of comparison are code brevity and syntax clarity
          (and hence maintainability and auditability) as well as performance.
        All performance tests are carried out using free and open-source compilers.
        In the case of Python, a significant performance gain is observed when switching from the standard 
          interpreter (CPython) to the PyPy implementation of Python.
        Entire source code of all three implementations is embedded in the text and is licensed
          under the terms of the GNU GPL license.
